Multiple testing with logical dependencies

### 2013-08-15 paper/draft.tex

\documentclass[a4paper,12pt]{article}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{graphicx}
%\usepackage{titlesec}
\usepackage{multirow}
\setlength\parindent{0in}
\usepackage[hdivide={2cm,*,2cm},vdivide={1in,*,1in}]{geometry}
\usepackage{setspace}
\doublespacing
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathrsfs}
\newcommand{\ud}{\, {\rm d} \kern-.015em }
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{comment}{Comment}
\newtheorem{lemma}{Lemma}
\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
\newtheorem{bsp}{Example}
\usepackage{natbib}
\usepackage{color}
\newenvironment{proof}[1][Proof]{\noindent\textbf{#1:} }{}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\usepackage{authblk}
\usepackage{lineno}
%\titlelabel{\thetitle.\quad}
\newcommand{\gmcp}{\mathcal{G}}

@@

\begin{proposition}{Properties of $M$ (Welsh, 2010)}
\label{the:cyclemat}
  \begin{enumerate}
  \item The cycles of $G$ are the circuits of $M$ 
  \item The spanning forests of $G$ are the bases of $M$
  \item If $G$ is connected the bases of $M$ are the spanning trees of $G$
  \item A set $X$ of edges of $G$ is independent in $M$ if and only if
    $X$ contains no cycle
  \item The rank of $M$ is $|V(G)| - k(G)$ where $k(G)$ denotes the
    number of connected components in $G$
  \item For any subset $A \subseteq E(G)$ the rank of $A$ in $M$ is
    given by
    \begin{displaymath}
      \rho_G(A) = |V(A)| - k(A)
    \end{displaymath}
    where $V(A)$ and $k(A)$ denote the set of vertices and number of
    connected componenents in the subgraph of $G$ induced by $A$
  \item Loops, and parallel edges correspond in $G$ and $M$
  \item Let $A \subset E(G)$, let $e \in E(G)\setminus A$. Then $e$
    belongs to the closure of $A$ in $M(G)$ if and only if there is a
    cycle $C$ of $G$ with
    \begin{displaymath}
      e \in C \subseteq A \cup e.
    \end{displaymath}

  \end{enumerate}
\end{proposition}

@@

Accordingly all porperties given in \ref{the:cyclemat} also hold for
the matroid on exhaustive sets.

@@

\begin{theorem}
  Consider a system of logically dependent hypotheses $\mathscr{H}$
  with dependence relation $\sim$ and associated matroid
  $M(\mathscr{H})$. Assume that $M(\mathscr{H})$ neither contains
  loops nor parallels. Consider a hierarchical testing procedure that
  tests $H_{i}$ at level $\alpha$ according to a prefixed
  order. Without loss of generality assume that $H_i$ are indexed
  according to the fixed rejection sequence $(1,...,n)$. Given 
  that hypotheses with indeces $1$ through $r$ have been
  rejected and if for $r+1$ to $r+s$ holds
  \begin{equation}
    \label{eq:cond.hierarchical}
    \forall 1 \leq l < k \leq s: \; \exists i \leq r: i \sim \{l,k\},
  \end{equation}
  hypotheses $H_{r+1}$ through $H_{r+s}$ can be tested simultaneously
  at full level $\alpha$.
\end{theorem}

\begin{proof}
  We show that given $p_{r+k} \leq \alpha$ for some $1 \leq k \leq s$
  all exhaustive sets $E \in \mathscr{L}_{r+k} = \{E \in \mathscr{L}:
  r+k \in E\}$ are rejected by the stepwise procedure. Since $p_{r+k}
  \leq \alpha$ implies rejection of all $E$ such that $\min E \geq
  r+k$, it remains to be shown that the stepwise procedure rejects
  $H_E$ for all exhaustive sets with $\min E < r+k$. Note that $\{E
  \in \mathscr{L}: \min E < r+k\} = \overline{\underline{E}}_1^r \cup
  \overline{\underline{E}}^{r+k-1}_{r+1}$ where
  $\overline{\underline{E}}^b_a := \{\sigma I: \text{for all } I
  \subseteq S, a \leq \min I \leq b\}$. For $ E \in
  \overline{\underline{E}}_1^r$ follows since $p_i \leq \alpha$ for $i
  \leq r$.

  Consider any set $I$ with $r < \min I < k$ then there is an $i \sim
  \{\min I,k\}$ with $i \leq r$. Consequently, $i \in \sigma \{\min
  I,k\}$ and also $\sigma I$. Therefore, we have $i \in E$ for all $E
  \in \overline{\underline{E}}^{r+k-1}_{r+1}$. Rejection of these sets
  follows from rejection of $H_i$, $i \leq r$, which completes the
  proof.
\end{proof}

>>>>

\documentclass[a4paper,12pt]{article}
\usepackage{amsthm}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{graphicx}
%\usepackage{titlesec}
\usepackage{multirow}
\setlength\parindent{0in}
\usepackage[hdivide={2cm,*,2cm},vdivide={1in,*,1in}]{geometry}
\usepackage{setspace}
\doublespacing
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathrsfs}
\newcommand{\ud}{\, {\rm d} \kern-.015em }
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{comment}{Comment}
\newtheorem{lemma}{Lemma}
\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
\newtheorem{bsp}{Example}
\usepackage{natbib}
\usepackage{color}

%\newenvironment{proof}[1][Proof]{\noindent\textbf{#1:} }{}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\usepackage{authblk}
\usepackage{lineno}
%\titlelabel{\thetitle.\quad}
\newcommand{\gmcp}{\mathcal{G}}

@@

\begin{proposition}{Properties of $M$ (Welsh, 2010)}
  The following properties hold for the cycle matroid of a graph $G$:
  \begin{enumerate}
  \item The cycles of $G$ are the circuits of $M$ 
  \item The spanning forests of $G$ are the bases of $M$
  \item If $G$ is connected the bases of $M$ are the spanning trees of $G$
  \item A set $X$ of edges of $G$ is independent in $M$ if and only if
    $X$ contains no cycle
  \item The rank of $M$ is $|V(G)| - k(G)$ where $k(G)$ denotes the
    number of connected components in $G$
  \item For any subset $A \subseteq E(G)$ the rank of $A$ in $M$ is
    given by
    \begin{displaymath}
      \rho_G(A) = |V(A)| - k(A)
    \end{displaymath}
    where $V(A)$ and $k(A)$ denote the set of vertices and number of
    connected componenents in the subgraph of $G$ induced by $A$
  \item Loops, and parallel edges correspond in $G$ and $M$
  \item Let $A \subset E(G)$, let $e \in E(G)\setminus A$. Then $e$
    belongs to the closure of $A$ in $M(G)$ if and only if there is a
    cycle $C$ of $G$ with
    \begin{displaymath}
      e \in C \subseteq A \cup e.
    \end{displaymath}

  \end{enumerate}
\label{the:cyclemat}
\end{proposition}

@@

Accordingly all porperties given in Proposition \ref{the:cyclemat} also hold for
the matroid on exhaustive sets.

@@

\begin{theorem}
  Consider a system of logically dependent hypotheses $\mathscr{H}$
  with dependence relation $\sim$ and associated matroid
  $M(\mathscr{H})$.   Assume that $M(\mathscr{H})$ neither contains loops nor
  parallels. Assume that hypotheses $H_1$ through $H_r$ have been
  rejected. Consider that hypotheses $H_{r+1}$ through $H_{r+t}$ are to
  be tested at level $\alpha$ according to a prefixed order.
  If for some $1 \leq s \leq t$ holds
  \begin{equation}
    \label{eq:cond.hierarchical}
    \forall 1 \leq l < k \leq s: \; \exists i \leq r: i \sim \{(r+l),(r+k)\},
  \end{equation}
  hypotheses $H_{r+1}$ through $H_{r+s}$ can be tested simultaneously
  at full level $\alpha$.
  \begin{equation}
    \label{eq:cond.hierarchical}
    \forall 1 \leq l < k \leq s: \; \exists i \leq r: i \sim \{r+l,k\},
  \end{equation}
  hypotheses $H_{r+1}$ through $H_{r+s}$ can be tested simultaneously
  at full level $\alpha$.
\end{theorem}

\begin{proof}
  We show that given $p_{r+k} \leq \alpha$ for some $1 \leq k \leq s$
  all exhaustive sets $E \in \mathscr{L}_{r+k} = \{E \in \mathscr{L}:
  r+k \in E\}$ are rejected by the stepwise procedure. We have
  $\mathscr{L}_{r+k} = \{\sigma I:I \subseteq S, (r+k) \in
  I\}$. $p_{r+k} \leq \alpha$ implies rejection of all $I \subseteq S$ such that
  $\min I = r+k$. It remains to be shown that the stepwise procedure
  rejects $H_E$ for all exhaustive sets with $\min E < r+k$. We have 
  $\{E \in \mathscr{L}_{r+k}: \min E < r+k\} = \{\sigma I: I \subseteq
  S, \min I \leq r\} \cup \{\sigma I: I \subseteq S, r < \min I <
  r+k\}$. For all $E \in \{\sigma I: I \subseteq
  S, \min I \leq r\}$ rejection of $H_E$ follows from rejection of
  $H_i$, $i \leq r$.

  Consider any set $I$ with $r < \min I < r+k$ then there is an $i
  \leq r$ such that $i \sim \{\min I,k\}$. Consequently, $i \in \sigma
  \{\min I,k\} \subseteq \sigma I$. Therefore, we have $i \in E$ for
  all $E \in \{\sigma I: I \subseteq S, r < \min I < r+k\}$. Rejection
  of the corresponding intersection hypotheses follows from rejection
  of $H_i$, $i \leq r$, which completes the proof.
\end{proof}
